Demers Cartogram with Rivers

### 2024-04-28 paper/main.tex
fix: table border
chore: add keywords
feat: JOVI latex template

\documentclass[Afour,sagev,times]{sagej}

@@

% \include{preamble/preamble.main}

@@

      \setlength{\intextsep}{3pt}
      \setlength{\columnsep}{3pt}
      \begin{wrapfigure}{r}{0.4\columnwidth}
        \vspace{-15pt}
        \begin{center}
          \includegraphics[width=0.38\columnwidth]{"#1".png}
        \end{center}
      \end{wrapfigure}
      #2

@@

% \include{preamble/preamble.math}
\usepackage{amsmath,bm}
\usepackage{amssymb}

@@

\usepackage[colorlinks,citecolor=red,urlcolor=red]{hyperref}

@@

@@

@@

\begin{abstract}
    Cartograms serve as representations of geographical and abstract data, employing a value-by-area mapping technique.
    As a variant of the Dorling cartogram, the Demers cartogram utilizes squares instead of circles to represent regions.
    This alternative approach allows for a more intuitive comparison of regions, utilizing screen space more efficiently.
    However, a drawback of the Dorling cartogram and its variants lies in the potential displacement of regions from their original positions, ultimately compromising legibility, readability, and accuracy.
    To tackle this limitation, we propose a novel hybrid cartogram layout algorithm that incorporates topological elements, such as rivers, into Demers cartograms.
    The presence of rivers significantly impacts both the layout and visual appearance of the cartograms.
    Through a user study conducted on an Electronic Health Records (EHR) dataset, we evaluate the efficacy of the proposed hybrid layout algorithm.
    The obtained results illustrate that this approach successfully retains key aspects of the original cartogram while enhancing legibility, readability, and overall accuracy.
\end{abstract}

\keywords{Cartogram, Demers Cartogram}

@@

\begin{samepage}

@@

    \begin{figure}[b!]
        \centering
        \includegraphics[width=\linewidth,keepaspectratio]{cover.png}
        \caption{The River Thames passing through a cartographic representation of the NHS CCGs in London and surrounding areas.}
        \label{fig:cover}
    \end{figure}

\end{samepage}

@@

    {
        \renewcommand{\arraystretch}{1.5}
        \begin{table*}[!tb]
            \centering
            \resizebox{\textwidth}{!}{
                \begin{tabulary}{\textwidth}{|*{4}{l|}r|c|}
                    \hhline{~|*{4}{-}|~}
                    \multicolumn{1}{c|}{\textbf{Literature}} &
                    \textbf{Cartogram Type(s)} &
                    \textbf{Geographic Region(s)} &
                    \textbf{Number of Nodes} &
                    \multicolumn{1}{c}{\textbf{Year}} \\
                    \hline

@@

 {
  \begin{figure}[b!]
      \centering
      \includegraphics[width=0.6\columnwidth]{ccg.png}
      \caption{A map of 135 CCGs in England as of 2020, obtained from the Open Geography Portalx \cite{opengeographyportalxOpen} with EPSG:4326 (WGS84 - World Geodetic System) as the Coordinate Reference System (CRS).}
      \label{fig:ccg}
  \end{figure}
 }

@@

{
    \begin{figure*}[tb!]
        \centering
        \includegraphics[width=0.8\textwidth,height=\textheight,keepaspectratio]{flowchart.png}
        \caption{An overview of our hybrid layout algorithm incorporating rivers.
            See also \Cref{alg:UpdateLayout} in Section \ref{sec:main} for more detail.
            See \Cref{fig:flowchart-stalemate} for the logic of processing a stalemate.
            For illustration purposes, we show the rendered views alongside the logical views representing the actual computation.}
        \label{fig:flowchart}
    \end{figure*}
}

{
    \begin{figure}[tb!]
        \centering
        \includegraphics[width=0.8\columnwidth,keepaspectratio]{river_resolution.png}
        \caption{The resolution of rivers can be dynamically adjusted by the user.
            (A) shows River Thames at its original resolution with 10,170 edges.
            (B) shows the river at a reduced resolution of 49 edges.
            We further smooth the river by removing 19 vertices in dense areas, as shown in (C).
            The reduced resolution preserves the majority of River Thames' original shape and improves the performance of our river intersection tests.}
        \label{fig:river resolution}
    \end{figure}
}

@@

@@

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{flowchart stalemate.png}
    \caption{A flowchart illustration of stalemate processing.
    See \Cref{subsec:{Process Stalemates}}, \Cref{fig:stalemate}, and \Cref{fig:corridor} for more detail.}
    \label{fig:flowchart-stalemate}
\end{figure}
}

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{stalemate.png}
    \caption{A stalemate: when a node's translation path $ \nodeVectorCT $ (iteration 1) intersects a river $ \stalemateMax $ times.
        The node is translated back to its previous position (iteration 2).
        A stalemate can occur when the area is congested and the node cannot translate to a new position without intersecting a river.}
    \label{fig:stalemate}
\end{figure}
}

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{corridor.png}
    \caption{A stalemate occurs when a node's translation path $ \nodeVectorCT $ intersects a river for $ \stalemateMax $ times, as shown in (A).
        To address this, we derive a corridor (orange rectangle in (E)) based on $ \node $ and $ \nodeFNOR $.
        All nodes within the corridor are translated based on $ \nodeVectorTC $, such that $ \nodeVectorNNn = \nodeVectorNinNinn $.
        For clarity in the illustration, we place nodes sparsely in this figure.}
    \label{fig:corridor}
\end{figure}
}

@@

@@

    {
        \begin{figure*}[tb!]
            \centering
            \includegraphics[width=0.9\textwidth,keepaspectratio]{UI.png}
            \caption{A screenshot of the user interface.
            User options are provided to adjust the terminating conditions (size and error), color mapping, visibility of nodes and rivers.
            Other options include the ability to control the overlap removal behavior: rivers can be static or dynamic.
            See \Cref{subsec:{UserOptions}} for more on user options.
            In this figure, $ \nodeCartographicErrorMax $ = 1.875\%, and an $ \nodeTopologicalError $ of 9.63\% is eliminated.}
            \label{fig:overview}
        \end{figure*}
    }

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{task.png}
            \caption{A sample location task for participants.
                The left shows the choropleth map, and the right shows the corresponding cartogram.
                Both images show the three longest rivers in England, and color is mapped to CCG population.
                The target CCG blinks on the choropleth (shown in black), and participants are asked to identify this CCG on the cartogram.
                In this figure, $ \nodeCartographicErrorMax $ = 1.875\% , and an $ \nodeTopologicalError $ of 6.67\% is eliminated.
            }
            \label{fig:task}
        \end{figure}
    }

@@

{
\begin{figure}[b!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{accuracy.png}
    \caption{In the bar chart, the y-axis shows the average accuracy rate of locating CCGs with and without rivers for user study participants.
        The x-axis shows the four target CCGs, as described in Procedure P3.}
    \label{fig:task-acc}
\end{figure}
}

@@

    {
        \begin{figure}[t!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{rt.png}
            \caption{In the bar chart, the y-axis shows the average response time for locating CCGs with and without rivers for user study participants.
                The x-axis shows the four target CCGs, as described in Procedure P3.}
            \label{fig:task-rt}
        \end{figure}
    }

@@

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{likert.png}
    \caption{The stacked bar chart shows the user study participant responses of Likert Scale questions.}
    \label{fig:likert}
\end{figure}
}

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=0.8\columnwidth,keepaspectratio]{extreme.png}
            \caption{Due to color and relative location, we believe the CCGs in the black circle are easier to locate.}
            \label{fig:extreme}
        \end{figure}
    }

@@

\urlstyle{same}
\bibliographystyle{plainnat}
\bibliography{references}

\cleardoublepage

\section{Appendix}
\appendix

@@

{
\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{import_rivers.png}
    \caption{QGIS interface, with River Trent, River Great Ouse, and River Thames (from top to bottom) imported.}
    \label{fig:import_rivers}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{import_ccgs.png}
    \caption{QGIS interface, with all NHS CCGs imported.}
    \label{fig:import_ccgs}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{unify_crs.png}
    \caption{QGIS interface, showing the unified CRS (OSGB36) for both layers.}
    \label{fig:unify_crs}
\end{figure}
}

@@

{
\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{export_rivers.png}
    \caption{QGIS interface, exporting all rivers using the OSGB36 CRS in GeoJSON.}
    \label{fig:export_rivers}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{export_ccgs.png}
    \caption{QGIS interface, exporting all NHS CCGs using the OSGB36 CRS in GeoJSON.}
    \label{fig:export_ccgs}
\end{figure}

@@

{
\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth]{export_topojson.png}
    \caption{Mapshaper interface, merging all rivers with NHS CCGs into one layer, and export the merged layer in TopoJSON.}
    \label{fig:export_topojson}
\end{figure}
}

@@

\Cref{table:pre-processing_result} shows the preprocessing result.
The reduction in file size is significant and greatly reduces the initialization time of our implementation.

    {
        \renewcommand{\arraystretch}{1.5}
        \begin{table}[H]
            \centering
            \resizebox{\columnwidth}{!}{
                \begin{tabulary}{\columnwidth}{|*{4}{l|}}
                    \hhline{~|*{3}{-}}
                    \multicolumn{1}{c|}{\textbf{Shapefile}} &
                    \cellcolor{Mycolor2}\textbf{Original} &
                    \cellcolor{Mycolor2}\textbf{GeoJSON} &
                    \cellcolor{Mycolor2}\textbf{TopoJSON} \\
                    \hline
                    Rivers & 2.0 MB (GeoJSON) & 1.4 MB & -  \\
                    \hline
                    NHS CCGs & 46.6 MB (.shp, Esri vector shapefile) & 140.2 MB & -  \\
                    \hline
                    Merged & - & - & 16.3 MB \\
                    \hline
                \end{tabulary}
            }
            \caption{The file size is reduced by 88.5\% from the original size.}
            \label{table:pre-processing_result}
        \end{table}
    }

% \clearpage
\section{Procedure: DeriveParallelEdge}
% \begin{noindent}

@@

        \end{algorithmic}
    \end{algorithm}
%\end{noindent}

@@

        \EndFor
        \State \Return{$ \nodeTopologicalError $}
        \EndProcedure
    \end{algorithmic}
\end{algorithm}
\vfill\eject

@@

        \EndProcedure
    \end{algorithmic}
\end{algorithm}
\vfill\eject

@@

%\end{noindent}
% \vfill\eject

@@

            \State \Return{$ False $}
            \EndProcedure
        \end{algorithmic}
    \end{algorithm}
    %\end{noindent}
% \vfill\eject

>>>>

\documentclass[iicol,sn-basic]{sn-jnl}% Basic Springer

\usepackage{graphicx}%
\usepackage{amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithmicx}%
%%%%

@@

@@

      \setlength{\intextsep}{3pt}
      \setlength{\columnsep}{3pt}
      \begin{wrapfigure}{r}{0.4\columnwidth}
        \vspace{-15pt}
        \begin{center}
          \includegraphics[width=0.38\columnwidth]{figure/"#1".png}
        \end{center}
      \end{wrapfigure}
      #2

@@

% \include{preamble/preamble.math}
\usepackage{amsmath,amssymb,bm}

@@

@@

\usepackage{hyperref}

@@

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

@@

%%=============================================================%%
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% \author*[1,2]{\fnm{Joergen W.} \spfx{van der} \sur{Ploeg} 
%%  \sfx{IV}}\email{iauthor@gmail.com}
%%=============================================================%%

\author*[1]{\fnm{Qiru} \sur{Wang}}\email{qiru.wang1@nottingham.ac.uk}

\author[1]{\fnm{Kai} \sur{Xu}}\email{kai.xu@nottingham.ac.uk}
\equalcont{These authors contributed equally to this work.}

\author[1]{\fnm{Robert} \sur{Laramee}}\email{robert.laramee@nottingham.ac.uk}
\equalcont{These authors contributed equally to this work.}

\affil[1]{\orgdiv{School of Computer Science}, \orgname{University of Nottingham}, \orgaddress{\street{University Park}, \city{Nottingham}, \postcode{NG7 2RD}, \state{England}, \country{United Kingdom}}}

%%==================================%%
%% Sample for unstructured abstract %%
%%==================================%%

\abstract{
    Cartograms serve as representations of geographical and abstract data, employing a value-by-area mapping technique.
    As a variant of the Dorling cartogram, the Demers cartogram utilizes squares instead of circles to represent regions.
    This alternative approach allows for a more intuitive comparison of regions, utilizing screen space more efficiently.
    However, a drawback of the Dorling cartogram and its variants lies in the potential displacement of regions from their original positions, ultimately compromising legibility, readability, and accuracy.
    To tackle this limitation, we propose a novel hybrid cartogram layout algorithm that incorporates topological elements, such as rivers, into Demers cartograms.
    The presence of rivers significantly impacts both the layout and visual appearance of the cartograms.
    Through a user study conducted on an Electronic Health Records (EHR) dataset, we evaluate the efficacy of the proposed hybrid layout algorithm.
    The obtained results illustrate that this approach successfully retains key aspects of the original cartogram while enhancing legibility, readability, and overall accuracy.
}

%%================================%%
%% Sample for structured abstract %%
%%================================%%

\keywords{Cartogram, Demers Cartogram, EHR Visualization, Visual Analytics}

%%\pacs[JEL Classification]{D8, H51}

%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}

@@

@@

\begin{figure}[b!]
    \centering
    \includegraphics[width=\linewidth,keepaspectratio]{figure/cover.png}
    \caption{The River Thames passing through a cartographic representation of the NHS CCGs in London and surrounding areas.}
    \label{fig:cover}
\end{figure}

@@

    {
        \renewcommand{\arraystretch}{1.5}
        \begin{table*}[!tb]
            \centering
            \resizebox{\textwidth}{!}{
                \begin{tabulary}{\textwidth}{|*{4}{l|}r|c|}
                    \hhline{~|*{4}{-}|~}
                    \multicolumn{1}{c|}{\textbf{Literature}} &
                    \textbf{Cartogram Type(s)} &
                    \textbf{Geographic Region(s)} &
                    \textbf{Number of Nodes} &
                    \multicolumn{1}{c|}{\textbf{Year}} \\
                    \hline

@@

 {
  \begin{figure}[b!]
      \centering
      \includegraphics[width=0.6\columnwidth]{figure/ccg.png}
      \caption{A map of 135 CCGs in England as of 2020, obtained from the Open Geography Portalx \cite{opengeographyportalxOpen} with EPSG:4326 (WGS84 - World Geodetic System) as the Coordinate Reference System (CRS).}
      \label{fig:ccg}
  \end{figure}
 }

@@

{
    \begin{figure*}[tb!]
        \centering
        \includegraphics[width=0.8\textwidth,height=\textheight,keepaspectratio]{figure/flowchart.png}
        \caption{An overview of our hybrid layout algorithm incorporating rivers.
            See also \Cref{alg:UpdateLayout} in Section \ref{sec:main} for more detail.
            See \Cref{fig:flowchart-stalemate} for the logic of processing a stalemate.
            For illustration purposes, we show the rendered views alongside the logical views representing the actual computation.}
        \label{fig:flowchart}
    \end{figure*}
}

{
    \begin{figure}[tb!]
        \centering
        \includegraphics[width=0.8\columnwidth,keepaspectratio]{figure/river_resolution.png}
        \caption{The resolution of rivers can be dynamically adjusted by the user.
            (A) shows River Thames at its original resolution with 10,170 edges.
            (B) shows the river at a reduced resolution of 49 edges.
            We further smooth the river by removing 19 vertices in dense areas, as shown in (C).
            The reduced resolution preserves the majority of River Thames' original shape and improves the performance of our river intersection tests.}
        \label{fig:river resolution}
    \end{figure}
}

@@

\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{figure/flowchart stalemate.png}
    \caption{A flowchart illustration of stalemate processing.
    See \Cref{subsec:{Process Stalemates}}, \Cref{fig:stalemate}, and \Cref{fig:corridor} for more detail.}
    \label{fig:flowchart-stalemate}
\end{figure}

@@

\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{figure/stalemate.png}
    \caption{A stalemate: when a node's translation path $ \nodeVectorCT $ (iteration 1) intersects a river $ \stalemateMax $ times.
        The node is translated back to its previous position (iteration 2).
        A stalemate can occur when the area is congested and the node cannot translate to a new position without intersecting a river.}
    \label{fig:stalemate}
\end{figure}

@@

\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{figure/corridor.png}
    \caption{A stalemate occurs when a node's translation path $ \nodeVectorCT $ intersects a river for $ \stalemateMax $ times, as shown in (A).
        To address this, we derive a corridor (orange rectangle in (E)) based on $ \node $ and $ \nodeFNOR $.
        All nodes within the corridor are translated based on $ \nodeVectorTC $, such that $ \nodeVectorNNn = \nodeVectorNinNinn $.
        For clarity in the illustration, we place nodes sparsely in this figure.}
    \label{fig:corridor}
\end{figure}

@@

    {
        \begin{figure*}[tb!]
            \centering
            \includegraphics[width=0.9\textwidth,keepaspectratio]{figure/UI.png}
            \caption{A screenshot of the user interface.
            User options are provided to adjust the terminating conditions (size and error), color mapping, visibility of nodes and rivers.
            Other options include the ability to control the overlap removal behavior: rivers can be static or dynamic.
            See \Cref{subsec:{UserOptions}} for more on user options.
            In this figure, $ \nodeCartographicErrorMax $ = 1.875\%, and an $ \nodeTopologicalError $ of 9.63\% is eliminated.}
            \label{fig:overview}
        \end{figure*}
    }

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/task.png}
            \caption{A sample location task for participants.
                The left shows the choropleth map, and the right shows the corresponding cartogram.
                Both images show the three longest rivers in England, and color is mapped to CCG population.
                The target CCG blinks on the choropleth (shown in black), and participants are asked to identify this CCG on the cartogram.
                In this figure, $ \nodeCartographicErrorMax $ = 1.875\% , and an $ \nodeTopologicalError $ of 6.67\% is eliminated.
            }
            \label{fig:task}
        \end{figure}
    }

@@

{
\begin{figure}[b!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{figure/accuracy.png}
    \caption{In the bar chart, the y-axis shows the average accuracy rate of locating CCGs with and without rivers for user study participants.
        The x-axis shows the four target CCGs, as described in Procedure P3.}
    \label{fig:task-acc}
\end{figure}
}

@@

    {
        \begin{figure}[t!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/rt.png}
            \caption{In the bar chart, the y-axis shows the average response time for locating CCGs with and without rivers for user study participants.
                The x-axis shows the four target CCGs, as described in Procedure P3.}
            \label{fig:task-rt}
        \end{figure}
    }

@@

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{figure/likert.png}
    \caption{The stacked bar chart shows the user study participant responses of Likert Scale questions.}
    \label{fig:likert}
\end{figure}
}

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=0.8\columnwidth,keepaspectratio]{figure/extreme.png}
            \caption{Due to color and relative location, we believe the CCGs in the black circle are easier to locate.}
            \label{fig:extreme}
        \end{figure}
    }

@@

\begin{appendices}

@@

    {
    \begin{figure}[H]
        \centering
        \includegraphics[width=\columnwidth]{figure/import_rivers.png}
        \caption{QGIS interface, with River Trent, River Great Ouse, and River Thames (from top to bottom) imported.}
        \label{fig:import_rivers}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[width=\columnwidth]{figure/import_ccgs.png}
        \caption{QGIS interface, with all NHS CCGs imported.}
        \label{fig:import_ccgs}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[width=\columnwidth]{figure/unify_crs.png}
        \caption{QGIS interface, showing the unified CRS (OSGB36) for both layers.}
        \label{fig:unify_crs}
    \end{figure}
    }

@@

    {
    \begin{figure}[H]
        \centering
        \includegraphics[width=\columnwidth]{figure/export_rivers.png}
        \caption{QGIS interface, exporting all rivers using the OSGB36 CRS in GeoJSON.}
        \label{fig:export_rivers}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[width=\columnwidth]{figure/export_ccgs.png}
        \caption{QGIS interface, exporting all NHS CCGs using the OSGB36 CRS in GeoJSON.}
        \label{fig:export_ccgs}
    \end{figure}

@@

    {
    \begin{figure}[H]
        \centering
        \includegraphics[width=\columnwidth]{figure/export_topojson.png}
        \caption{Mapshaper interface, merging all rivers with NHS CCGs into one layer, and export the merged layer in TopoJSON.}
        \label{fig:export_topojson}
    \end{figure}
    }

@@

    \Cref{table:pre-processing_result} shows the preprocessing result.
    The reduction in file size is significant and greatly reduces the initialization time of our implementation. See \Cref{table:pre-processing_result}.

    {
    \renewcommand{\arraystretch}{1.5}
    \begin{table}[!tb]
        \centering
        \resizebox{\columnwidth}{!}{
            \begin{tabulary}{\columnwidth}{|*{4}{l|}}
                \hhline{~|*{3}{-}}
                \multicolumn{1}{c|}{\textbf{Shapefile}} &
                \cellcolor{Mycolor2}\textbf{Original} &
                \cellcolor{Mycolor2}\textbf{GeoJSON} &
                \cellcolor{Mycolor2}\textbf{TopoJSON} \\
                \hline
                Rivers & 2.0 MB (GeoJSON) & 1.4 MB & -  \\
                \hline
                NHS CCGs & 46.6 MB (.shp, Esri vector shapefile) & 140.2 MB & -  \\
                \hline
                Merged & - & - & 16.3 MB \\
                \hline
            \end{tabulary}
        }
        \caption{The file size is reduced by 88.5\% from the original size.}
        \label{table:pre-processing_result}
    \end{table}
    }

    \section{Procedure: DeriveParallelEdge}
    % \begin{noindent}

@@

@@

            \EndFor
            \State \Return{$ \nodeTopologicalError $}
            \EndProcedure
        \end{algorithmic}
    \end{algorithm}

@@

@@

@@

            \State \Return{$ False $}
            \EndProcedure
        \end{algorithmic}
    \end{algorithm}

\end{appendices}

\bibliography{references}
